---
title: "R Markdown exercise"
output:
  xaringan::moon_reader:
    css: [default, rd.css, rd-font.css, "hygge"]
    lib_dir: assets
    seal: false
    nature:
      highlightStyle: dracula
      countIncrementalSlides: false
      beforeInit: "macros.js"
---

class: inverse, center, middle

# Let's practice `r lc()`

![:custom_hr]()


```{r setup_04, include = FALSE}
source("_setup.R")
htmltools::tagList(
  xaringanExtra::use_clipboard(
    button_text = "<i class=\"fa fa-clipboard\"></i>",
    success_text = "<i class=\"fa fa-check\" style=\"color: #37abc8\"></i>",
  ),
  rmarkdown::html_dependency_font_awesome()
)
xaringanExtra::use_scribble()
```

<!-- rmarkdown::render("_04_practice.Rmd") -->


---

# Exercise

## Context

- *The goal of the exercise is to add and render a R Markdown document to the git repo you previously created.*

--

- *To do this, we will use data on Palmer penguins from [Dr. Kristen Gorman](https://www.uaf.edu/cfos/people/faculty/detail/kristen-gorman.php) and the [Palmer Station, Antarctica LTER](https://pal.lternet.edu/).*

--

- *Data are available through the [`palmerpenguin`](https://github.com/allisonhorst/palmerpenguins) R package.*

```{r palmer, eval = FALSE}
library(palmerpenguins)
data(package = 'palmerpenguins')
```

---

# Exercise

## Context

```{r load, echo = FALSE}
library(palmerpenguins)
```
```{r head}
head(penguins)
```

---

# Exercise

## Task

.font90[
**1)** Install the `palmerpenguins` R Package

**2)** Create a new R Markdown document (`.rmd`)

**3)** Write a .font80[**YAML**] header including the document title, the authors, the date, and output formats html, pdf and word with a table of content for each

**4)** Include a single section (level 1) and two subsections (level 2)
]


---

# Exercise

## Task

.font90[
**5)** In the first subsection:

  - Add paragraphs including normal and formatted text (italic, bold)

  - Add artwork from @allison_horst on palmer penguins found on the `palmerpenguins` R Package GitHub repository (https://github.com/allisonhorst/palmerpenguins) as a local image (for pdf output).

  - Add a footnote to the artwork that states: *"Artwork by @allison_horst"*

  - Add a code chunk that loads the `palmerpenguins` package and `penguins` dataset. Generate a table to visualize the first 20 lines of the dataset.
]

---

# Exercise

## Task

.font90[
**6)** In the second subsection:

  - Copy the following text and use inline code chunks to fill in the blanks:

    > The penguins dataset contains data on \_\_\_\_ individuals, \_\_\_\_ species, and from \_\_\_\_ islands. Across individuals, the mean flipper length is \_\_\_\_.

  - In the previous text, add a hyperlink to the `palmerpenguins` R Package GitHub repository when a user clicks on [penguins dataset](https://github.com/allisonhorst/palmerpenguins);

  - Add a code chunk that generates a scatterplot of flipper length on the x-axis and body mass on the y-axis.

**7)** Render `.html`, `.pdf` and `.docx` documents.
]


---
# Exercise

## Task

`r rfa("info-circle")` Cannot render `.pdf` file, try:

```{R, eval = FALSE}
install.packages("tinytex")
tinytex::install_tinytex()
```


---

# Exercise

## Solution

Load solution file here: [`r rfa("database")`](https://github.com/inSilecoInc/git_markdown/blob/main/exercise1.rmd)

